Dependent Object Types

### 2012-09-03 doc/candidacy/report.tex
ML rev

Path-dependent types are a key concept in the DOT calculus, and a
unifying concept of the three papers we choose to study. A {\it
  dependent type} is a type which depends on a term. A {\it
  path-dependent type} is a limited form of dependent type, in which a
type depends on a path: a chain of immutable fields or
variables. Path-dependent types arise when terms, usually objects, can
have types as members. Abstract type members, together with explicit
selftypes and modular mixin composition have been identified as key
abstractions for the construction of reusable components~\cite{SCA}.

@@

Scala's abstract types have close resemblances to abstract types of
signatures in these ML-like module systems. In particular, in their
calculus, there's a form of dependent type, since translucent sums are
terms that may contain types. Compared to path-dependent types
as found in Scala, these are more limited because recursive references
and bounded quantifications are not allowed.

>>>>

Path-dependent types are a key concept in the DOT calculus, and a
unifying concept of the three papers we choose to study. A {\it
  dependent type} is a type which depends on a term. A {\it
  path-dependent type} is a limited form of dependent type, in which a
type depends on a path: a chain of immutable fields or
stable values. Path-dependent types arise when terms, usually objects, can
have types as members. Abstract type members, together with explicit
selftypes and modular mixin composition have been identified as key
abstractions for the construction of reusable components~\cite{SCA}.

@@

Scala's abstract types have close resemblances to abstract types of
signatures in these ML-like module systems. In particular, in their
calculus, there's a form of dependent type, since translucent sums are
terms that may contain types. More concretely, their so-called VALUE
rules enable a translucent sum to be given a more precise type by
referring to the names of its type members with a path selection --
this ability based on path-dependent types is not only essential for
breaking the dependencies between (sub)fields but also critical for
the propagation of typing information. Compared to Scala, these
path-dependent types are more limited because recursive references and
bounded quantifications are not allowed.

### 2012-09-03 doc/candidacy/slides.tex
section titles
sym
ML rev

@@

@@

\begin{description}[path-dependent type]
\item[path-dependent type] limited form of \emph{dependent type}, in which a type depends on a \emph{path}
\item[dependent type] a type which depends on a term
\item[path] a chain of immutable fields or variables
\end{description}

\inputminted[frame=lines,fontsize=\footnotesize]{scala}{intro.scala}

>>>>

\title{Dependent Object Types}
\subtitle{EDIC Candidacy Exam}
\author{Nada Amin}
\institute{LAMP, I\&C, EPFL}
\date{September 12, 2012}

@@

\frame{\titlepage}

\section{Introduction}

@@

\begin{description}[path-dependent type]
\item[path-dependent type] limited form of \emph{dependent type}, in which a type depends on a \emph{path}
\item[dependent type] a type which depends on a term
\item[path] a chain of immutable fields or stable values
\end{description}

\inputminted[frame=lines,fontsize=\footnotesize]{scala}{intro.scala}
\end{frame}

\begin{frame}{Selected Papers}
\begin{enumerate}
\item {\it A Type-Theoretic Approach to Higher-Order
  Modules with Sharing}\\{\footnotesize\textcolor{gray}{by Robert Harper and Mark
  Lillibridge}}\begin{itemize}
\item calculus for modules in the ML tradition
\item modules are first-class values
\end{itemize}
\item {\it Tribe: a simple virtual class calculus}\\
  {\footnotesize\textcolor{gray}{by Dave Clarke, Sophia Drossopoulou, James Noble and Tobias Wrigstad}}\begin{itemize}
\item calculus for virtual classes
\item paths are types, and types are ``generalized'' paths
\end{itemize}
\item {\it A Nominal Theory of Objects with Dependent
  Types}\\{\footnotesize\textcolor{gray}{by Martin Odersky, Vincent Cremet, Christine R{\"o}ckl and
  Matthias Zenger}}\begin{itemize}
\item calculus unifying advanced object-oriented and module systems
\item foundation for Scala
\end{itemize}
\end{enumerate}
\end{frame}

\section{Survey of Selected Papers}

\subsection{``Translucent'' ML}

\subsection{Tribe Calculus}

\subsection{${\nu}Obj$}

\section{Proposal}
